\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=0.75in}
\usepackage{enumitem}
\setlist{noitemsep}

\begin{document}

% Cabeçalho
\begin{center}
    {\Huge \textbf{ Alex Nascimento }} \\
    \vspace{2mm}
    LOGISTICS | TRANSPORTATION AND STORAGE | E-COMMERCE \\
    Indaiatuba, São Paulo | (19) 98290-7060 | alex_nascto@hotmail.com \\
    linkedin.com/in/alexnascimento1980 | github.com/SeuUsuario
\end{center}

% Resumo
\section*{ Summary }
\begin{itemize}
    
    
        \item Experience in scheduling and strategic delivery planning, ensuring efficiency and punctuality.
    
        \item Skill in shipment tracking, offering visibility and security in national operations.
    
        \item Proficiency in freight negotiation and fleet management for an uninterrupted supply chain.
    
\end{itemize}

% Experiência Profissional
\section*{ Professional Experience }

    \noindent \textbf{ DHL Supply Chain } \hfill 05/2019 -- 09/2024 \\
    \textit{ Transport Assistant }
    \begin{itemize}
        
        
            \item Focused on product collection services sold via sales application (Customer's First Mile).
        
            \item Trained third-party drivers to provide excellent service according to client standards.
        
            \item Managed the partner driver base to maintain interest and operational availability.
        
    \end{itemize}
    \vspace{2mm}

    \noindent \textbf{ West Side Viagens E Turismo (Grupo Belarmino) } \hfill 07/2018 -- 05/2019 \\
    \textit{ Traffic Assistant }
    \begin{itemize}
        
        
            \item Controlled schedules and ensured adherence to shift start times for charter line drivers.
        
            \item Monitored traffic and coordinated backup vehicles in case of delays.
        
            \item Managed and archived tachograph discs and fleet logbooks.
        
    \end{itemize}
    \vspace{2mm}

    \noindent \textbf{ Atual Solística / AGV Logística } \hfill 01/2012 -- 03/2017 \\
    \textit{ Logistics Analyst }
    \begin{itemize}
        
        
            \item Shipper customer service and loading demand analysis.
        
            \item Freight quoting and management using TMS and ERP systems.
        
            \item Driver/vehicle registration and security clearance.
        
    \end{itemize}
    \vspace{2mm}


% Formação Acadêmica
\section*{ Education }

    \noindent \textbf{ UNIVESP } \hfill 2024 -- Present \\
    \textit{ Bachelor's in Data Science } \\
    Status: 6th semester
    \vspace{2mm}


% Habilidades
\section*{ Skills }
\noindent \textbf{ Technical : } Python, SQL, Power BI, Pacote Office, ERP (TMS e SAP) \\
\textbf{ Languages : } 

    English (Beginner)


\end{document}